\begin{thebibliography}{33}
%\providecommand{\natexlab}[1]{#1}
\bibitem[Abraham et~al.(2011)Abraham, Delling, Fiat, Goldberg, and
  Werneck]{AbrahamDFGW11}
%I.~Abraham, D.~Delling, A.~Fiat, A.~V.~Goldberg, and R.~F.~Werneck.
I.~Abraham et al.
\newblock {VC}-dimension and shortest path algorithms.
\newblock ICALP'11, 2011.

\bibitem[Aingworth et~al.(1999)Aingworth, Chekuri, Indyk, and
  Motwani]{AingwordCIM99}
%D.~Aingworth, C.~Chekuri, P.~Indyk, and R.~Motwani.
D.~Aingworth et al.
\newblock Fast estimation of diameter and shortest paths (without matrix
  multiplication).
\newblock \emph{SIAM J.~on Comput.}, 28\penalty0 (4):\penalty0 1167--1181, 1999.

\bibitem[Anthonisse(1971)]{Anthonisse71}
J.~M. Anthonisse.
\newblock The rush in a directed graph.
\newblock TR BN 9/71, Stichting Mathematisch Centrum, Amsterdam,
  Netherlands, 1971.

\bibitem[Bader et~al.(2007)Bader, Kintali, Madduri, and Mihail]{BaderKMM07}
%D.~A.~Bader, S.~Kintali, K.~Madduri, and M.~Mihail.
D.~A.~Bader et al.
\newblock Approximating betweenness centrality.
\newblock WAW'07, 2007.

\bibitem[Barab{\'a}si and Albert(1999)]{BarabasiA99}
A.-L. Barab{\'a}si and R.~Albert.
\newblock Emergence of scaling in random networks.
\newblock \emph{Science}, 286\penalty0 (5439):\penalty0 509--512, 1999.

\bibitem[Boitmanis et~al.(2006)Boitmanis, Freivalds, Ledins, and
  Opmanis]{BoitmanisFL06}
%K.~Boitmanis, K.~Freivalds, P.~Ledins, and R.~Opmanis.
K.~Boitmanis et al.
\newblock Fast and simple approximation of the diameter and radius of a graph.
\newblock WEA'06, 2006.

\bibitem[Borgatti and Everett(2006)]{BorgattiE06}
S.~P.~Borgatti and M.~G.~Everett.
\newblock A graph-theoretic perspective on centrality.
\newblock \emph{Soc.~Net.}, 28\penalty0 (4):\penalty0 466--484, 2006.

\bibitem[Brandes(2001)]{Brandes01}
U.~Brandes.
\newblock A faster algorithm for betweenness centrality.
\newblock \emph{J. Math.~Sociol.}, 25\penalty0 (2):\penalty0 163--177, 2001.

\bibitem[Brandes(2008)]{Brandes08}
U.~Brandes.
\newblock On variants of shortest-path betweenness centrality and their generic
  computation.
\newblock \emph{Soc.~Net.}, 30\penalty0 (2):\penalty0 136--145, 2008.

\bibitem[Brandes and Pich(2007)]{BrandesP07}
U.~Brandes and C.~Pich.
\newblock Centrality estimation in large networks.
\newblock \emph{Intl.~J. Bifurc.~and Chaos}, 17\penalty0 (07):\penalty0
2303--2318, 2007.

\bibitem[Cs\'{a}rdi and Nepusz(2006)]{igraph}
G.~Cs\'{a}rdi and T.~Nepusz.
\newblock The igraph software package for complex network research.
\newblock \emph{InterJournal}, Complex Sys.:\penalty0 1695, 2006.
\newblock URL \url{http://igraph.sf.net}.

\bibitem[Dolev et~al.(2010)Dolev, Elovici, and Puzis]{DolevEP10}
%S.~Dolev, Y.~Elovici, and R.~Puzis.
S.~Dolev et al.
\newblock Routing betweenness centrality.
\newblock \emph{J. ACM}, 57\penalty0 (4):\penalty0 25:1--25:27, May 2010.

\bibitem[Eppstein and Wang(2004)]{EppsteinW04}
D.~Eppstein and J.~Wang.
\newblock Fast approximation of centrality.
\newblock \emph{J.~Graph Alg.~and Appl.}, 8\penalty0
  (1):\penalty0 39--45, 2004.

\bibitem[Freeman(1977)]{Freeman77}
L.~C. Freeman.
\newblock A set of measures of centrality based on betweenness.
\newblock \emph{Sociometry}, 40:\penalty0 35--41, 1977.

\bibitem[Geisberger et~al.(2008)Geisberger, Sanders, and
  Schultes]{GeisbergerSS08}
%R.~Geisberger, P.~Sanders, and D.~Schultes.
R.~Geisberger et al.
\newblock Better approximation of betweenness centrality.
\newblock ALENEX'08, 2008.

\bibitem[Har-Peled and Sharir(2011)]{HarPS11}
S.~Har-Peled and M.~Sharir.
\newblock Relative $(p,\varepsilon)$-approximations in geometry.
\newblock \emph{Discr.~\& Comput.~Geom.}, 45\penalty0 (3):\penalty0
  462--496, 2011.

\bibitem[Hoeffding(1963)]{Hoeffding63}
W.~Hoeffding.
\newblock Probability inequalities for sums of bounded random variables.
\newblock \emph{J.~Am.~Stat.~Assoc.}, 58\penalty0
  (301):\penalty0 13--30, 1963.

\bibitem[Jacob et~al.(2005)Jacob, Kosch{\"u}tzki, Lehmann, Peeters, and
  Tenfelde-Podehl]{JacobKLPT05}
%R.~Jacob, D.~Kosch{\"u}tzki, K.~Lehmann, L.~Peeters, and D.~Tenfelde-Podehl.
R.~Jacom et al.
\newblock Algorithms for centrality indices.
\newblock \emph{LNCS}, 3418:\penalty0 62--82, 2005.

\bibitem[Kaindl and Kainz(1997)]{KaindlK97}
H.~Kaindl and G.~Kainz.
\newblock Bidirectional heuristic search reconsidered.
\newblock \emph{J. Artif. Intell. Res.}, 7:\penalty0 283--317, 1997.

\bibitem[Kourtellis et~al.(2012)Kourtellis, Alahakoon, Simha, Iamnitchi, and
  Tripathi]{KourtellisASIT12}
%N.~Kourtellis, T.~Alahakoon, R.~Simha, A.~Iamnitchi, and R.~Tripathi.
Kourtellis et al.
\newblock Identifying high betweenness centrality nodes in large social
  networks.
\newblock \emph{Soc.~Net.~Analysis and Mining}, pages 1--16, 2012.

\bibitem[Kranakis et~al.(1997)Kranakis, Krizanc, Ruf, Urrutia, and
  Woeginger]{KranakisKRUW97}
%E.~Kranakis, D.~Krizanc, B.~Ruf, J.~Urrutia, and G.~Woeginger.
Kranakis et al.
\newblock The {VC}-dimension of set systems defined by graphs.
\newblock \emph{Discr. Appl. Math.}, 77\penalty0 (3):\penalty0
  237--257, 1997.

\bibitem[Li et~al.(2001)Li, Long, and Srinivasan]{LiLS01}
%Y.~Li, P.~M. Long, and A.~Srinivasan.
Y.~Li et al.
\newblock Improved bounds on the sample complexity of learning.
\newblock \emph{J.~Comp.~and~Sys.~Sci.}, 62\penalty0
  (3):\penalty0 516--527, 2001.

\bibitem[Lim et~al.(2011)Lim, Menasche, Ribeiro, Towsley, and Basu]{LimMRTB11}
%Y.-s. Lim, D.~Menasche, B.~Ribeiro, D.~Towsley, and P.~Basu.
Y.-s. Lim et al.
\newblock Online estimating the k central nodes of a network.
\newblock NSW'11, 2011

\bibitem[L\"{o}ffler and Phillips(2009)]{LofflerP09}
M.~L\"{o}ffler and J.~M. Phillips.
\newblock Shape fitting on point sets with probability distributions.
\newblock ESA'09, 2009.

\bibitem[Maiya and Berger-Wolf(2010)]{MaiyaBW10}
A.~Maiya and T.~Berger-Wolf.
\newblock Online sampling of high centrality individuals in social networks.
\newblock PAKDD'10, 2010.

\bibitem[Mitzenmacher and Upfal(2005)]{MitzenmacherU05}
M.~Mitzenmacher and E.~Upfal.
\newblock \emph{Probability and Computing: Randomized Algorithms and
  Probabilistic Analysis}.
\newblock Cambridge University Press, 2005.

\bibitem[Mohri et~al.(2012)Mohri, Rostamizadeh, and Talwalkar]{MohriRT12}
%M.~Mohri, A.~Rostamizadeh, and A.~Talwalkar.
M.~Mohri et al.
\newblock \emph{Foundations of Machine Learning}.
\newblock The MIT Press, 2012.

\bibitem[Newman(2010)]{Newman10}
M.~E.~J.~Newman.
\newblock \emph{Networks - An Introduction}.
\newblock Oxford University Press, 2010.

\bibitem[Pfeffer and Carley(2012)]{PfefferC12}
J.~Pfeffer and K.~M.~Carley.
\newblock k-centralities: local approximations of global measures based on
  shortest paths.
\newblock WWW'12, 2012.

\bibitem[Pohl(1969)]{Pohl69}
I.~Pohl.
\newblock \emph{Bidirectional Heuristic Search in Path Problems}.
\newblock PhD thesis, Stanford University, 1969.

%\bibitem[Riondato and Kornaropoulos(2013)]{RiondatoK13}
% M.~Riondato and E.~M.~Kornaropoulos
% \newblock Fast Approximation of Betweenness Centrality through Sampling.
\bibitem[Anonymous(2013)]{Anonymous13}
Anonymized for blind submission.

\bibitem[Roditty and Williams(2012)]{RodittyW12}
L.~Roditty and V.~V.~Williams.
\newblock Approximating the diameter of a graph.
\newblock \emph{CoRR abs/1207.3622}, 2012.

\bibitem[Sariy\"{u}ce et~al.(2013 (to appear))Sariy\"{u}ce, Saule, Kaya, and
  Catalyurek]{SaryuceSKC13}
%A.~E.~Sariy\"{u}ce, E.~Saule, K.~Kaya, and U.~V.~Catalyurek.
A.~E.~Sariy\"{u}ce et al.
\newblock Shattering and compressing networks for betweenness centrality.
\newblock SDM'13, 2013.

\bibitem[Vapnik and Chervonenkis(1971)]{VapnikC71}
V.~N.~Vapnik and A.~J.~Chervonenkis.
\newblock On the uniform convergence of relative frequencies of events to their
  probabilities.
\newblock \emph{Theory~of Prob.~and its Appl.}, 16\penalty0
  (2):\penalty0 264--280, 1971.

\end{thebibliography}

